How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-15 docs/PhysicsPaper/StokesErosion.tex
NM

>>>>

	\edit{Random configurations of circular bodies are initialized by a simulated-annealing algorithm. First, a list of radii are sampled from a Chi distribution. The radii are then rescaled to achieve the desired initial porosity. Next, the circular bodies are positioned randomly, which typically results in many overlapping bodies. To eliminate overlap, fictitious forces are introduced that act to repel bodies from one another and from domain boundaries. The force also has a stochastic component whose magnitude decreases with time. This algorithm allows the bodies to explore different configurations and eventually settle on one without any overlap between bodies.}
